---
title: "Iteration and listcolumn"
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(rvest)
set.seed(1)
```

## lists

```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```


```{r}
l = list(vec_numeric = 5:8,
         mat         = matrix(1:8, 2, 4),
         vec_logical = c(TRUE, FALSE),
         summary     = summary(rnorm(1000)))
l$vec_numeric[2]

l$vec_numeric

l[[1]]

l[[1]][1:3]
```

### for loops

```{r}
df = data_frame(
  a = rnorm(20, 3, 1),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)

is.list(df)
#data frames are actually a very specific kind of list

df[[2]]
```

Let's get a function.

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

We can apply the function to `df`.

```{r}
mean_and_sd(df[[1]])
mean_and_sd(df[[2]])
mean_and_sd(df[[3]])
mean_and_sd(df[[4]])
```

### Write a for-loop

i-placeholder
```{r}
output = vector("list", length = 4)

output[[1]] = mean_and_sd(df[[1]])
output[[2]] = mean_and_sd(df[[2]])
output[[3]] = mean_and_sd(df[[3]])
output[[4]] = mean_and_sd(df[[4]])

#simpler
for (i in 1:4) {
  output[[i]] = mean_and_sd(df[[i]])
}

output
```

### map statement

let's replace the `for` loop with `map`

```{r}
output = map(df, mean_and_sd)

output$a

df %>% 
  select(a, b, c) %>% 
  map(mean_and_sd)
```

Let's try a different function

```{r}
output = map(df, summary)
```

### map variant

```{r}
output = map_df(df, mean_and_sd)

map_dbl(df, median)
map_dfr(df, mean_and_sd, .id = "input")

output = map_dbl(df, median, .id = "input")

#map2(.x = input_1, .y = input_2, ~func(arg_1 = .x, arg_2 = .y))

```

lotr_data = map2_df(
  .x = cell_ranges, .y = movie_names, 
  ~lotr_load_and_tidy(path = "./data/LotR_Words.xlsx", range = .x, movie_name = .y))


### code syntax

be more specific in giving arguments to map
.x as a placeholder

```{r}
output = map(.x = df, ~ mean_and_sd(.x))

output = map(.x = df, ~ mean(x = .x, na.rm = FALSE))
```

### Revisiting Napoleon

```{r}
library(rvest)

read_page_reviews <- function(url) {
  
  h = read_html(url)
  
  title = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  data_frame(title, stars, text)
}
```


```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

reviews = map(vec_urls, read_page_reviews)

output = vector("list", 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

dynamite_reviews = bind_rows(output)

dynamite_reviews = map_df(vec_urls, read_page_reviews)
```

## List columns ...

```{r}
library(rnoaa)

weather = 
  meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2016-01-01",
                      date_max = "2016-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
#centralpark = weather %>% filter(...)

weather_nest = 
  weather %>% 
  nest(date:tmin)

#Alternative
weather %>% 
  group_by(name, id) %>% 
  nest()

weather_nest %>% pull(name)
weather_nest %>% pull(id)
weather_nest %>% pull(data)
```

Unnesting...

```{r}
weather_nest %>% 
  unnest()
```

look at LC elements

```{r}
weather_nest$data[[1]] %>% 
  filter(prcp == 0)

weather_nest$data[[3]] %>% 
  skimr::skim()
```

Fit a location-specific regression ...

```{r}
lm(tmax ~ tmin, data = weather_nest$data[[1]])
lm(tmax ~ tmin, data = weather_nest$data[[2]])
lm(tmax ~ tmin, data = weather_nest$data[[3]])
```

Write a function

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nest$data[[1]])

weather_lm_1 = function(i) {
  lm(tmax ~ tmin, data = weather_nest$data[[i]])
}

weather_lm_1(1)

#avoid the creation of a dedicated function 
map(weather_nest$data, ~lm(tmax ~ tmin, data = .x))
```

group_by + summerize doesn't work here(only works when outcome is a single number--mean/median)

```{r}
map(weather_nest$data, weather_lm)

#map_df not working here--output of lm is not a dataframe
```

Save output as a new list column

keep track of separate linear regression model of independent object

```{r}
lm_op = weather_nest %>% 
  mutate(lm_result = map(data, weather_lm))

lm_op$lm_result[[1]]

```

## A couple final examples

```{r, eval = FALSE}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
reviews = tibble(
  page = 1:5,
  url = str_c(url_base, page)
) %>% 
  mutate(reviews = map(url, read_page_reviews)) %>% 
  unnest()
```

```{r}
lotr_cell_ranges = 
  tibble(
    movie = c("fellowship_ring", "two_towers", "return_king"),
    cells = c("B3:D6", "F3:H6", "J3:L6")
  )
lotr_tidy = 
  lotr_cell_ranges %>% 
  mutate(
    word_data = map(cells, ~readxl::read_excel("./data/LotR_Words.xlsx", range = .x))
  ) %>% 
  unnest() %>% 
  janitor::clean_names() %>% 
  gather(key = sex, value = words, female:male) %>%
  mutate(race = tolower(race)) %>% 
  select(movie, everything(), -cells) 
```
